\chapter{Development of lattice-Boltzmann Modeling Tools for Ceramic Solid Breeders}\label{sec:modeling-lbm}
The volume-averaged approach of the CFD-DEM coupling is an effective and efficient method for solving transiently coupled helium flow and pebble interaction. However, there are cases when a complete knowledge of the tortuous flow of the interstitial helium is desired. But because the CFD-DEM solver does not resolve the pathways on the particle scale, knowledge of precise helium flow is not possible with that technique. Therefore we have also investigated a combination of DEM and with lattice-Boltzmann solvers. 

The lattice-Boltzmann approach to fluid simulations is a growing field of numerical modeling with a rich historical development. As the LBM approach is relatively unfamiliar, we will go through some of the notable evolutions of the modeling history and the background physics leading to the governing equations to be implemented numerically. Certainly this short study cannot do justice to a proper explanation of the underlying physics. References~\cite{Chen1998a,Viggen2009,Sukop2007,Chopard2002,succi2001lattice} should be read by those curious for excellent and thorough descriptions of the physics, modeling approaches, and applications of LBM theory to fluid dynamics problems.

In the rest of this chapter we introduce the core concepts behind the lattice-Boltzmann method, their application into numerical code, and finally a discussion of the solver used in this research.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{chapters/sections/lbm-modeling-intro.tex}
\input{chapters/sections/lbm-num-method.tex}
\input{chapters/sections/lbm-benchmark.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%